---
title: "Criminal Justice Dissertation Topic Analysis"
author: "Connor Concannon"
date: '2016-11-06'
tags: [R, NLP]
output: html_document
editor_options: 
  chunk_output_type: console
---

## Introduction

Months ago, I was perusing the [American Society of Criminology's](http://asc41.com) website and came across a [list of recent dissertations](http://www.asc41.com/graduates1.htm), including topics, authors, and instutitions.  

The list was interesting to me for a few reasons.  One, I need to begin thinking about a dissertation topic, and I would like to get a sense of recent dissertations, without having to actually read them.  Two, the list was an opportunity to do some exploratory analysis and use some techniques and packages that I am not too familiar with, namely web scraping.  And three, I could use this as an opportunity to publish a quick analysis and begin building a portfolio of analytical projects that are not necessarily work-related.  

First, load a bunch of libraries.

```{r setup, include=T,message=F,warning=F,echo=F}

pkg <- c('tidytext','rvest','stringr','dplyr','tm','SnowballC','wordcloud','DescTools',
'ggmap','Amelia','leaflet','highcharter','LDAvis','graph','tidyr','Rgraphviz','ggplot2')

library(lubripack)
lubripack(pkg)



```



## Scraping and Cleaning

Next, I take the url, extract the data and clean it up quite a bit.  I have never tried any webscraping, but rvest makes it seem easy.  I am sure this can be improved, chained into a neater workflow, errors removed, etc., but I am not striving for perfection.  This was the most frustrating part, as the page seems to lack a consistent format for the information.  I am most interested in the topics, so the rest is not a big deal.  The code is not too interesting, but can be [viewed here](https://github.com/concannon/ASCScraping/blob/master/rvest.R).  

After parsing out the various fields, I geocoded the institutions with ggmap::geocode



```{r,warning=F,message=F,echo=F, eval=F}
#get data
phds <- read_html('http://www.asc41.com/graduates1.htm')

d <- phds %>% 
  html_nodes('p , em , strong') %>% 
  html_text() %>% 
  #gsub('“','"',.) %>% 
  gsub('\r\n','',.) %>% 
  gsub("[\\]",'',.)


##Parse
#Years
yr <- "[1-9][0-9]{3}"

years <- str_locate_all(d,yr)
yearloc <- lapply(years,'[',1)
yearloc <- data.frame(yearLoc=unlist(yearloc))
years <- data.frame(Year=as.integer(str_extract(d,yr)))

#find first period
period <- str_locate_all(d,"\\.")
period <- lapply(period,'[',1)
period <- data.frame(PeriodLoc=unlist(period))


#find special characters
char <- str_locate_all(d,"\\?")
char <- lapply(char,'[',1)
char <- data.frame(CharLoc=unlist(char))
#str_sub(d,1,char$CharLoc)

#find first comma
comma <- str_locate_all(d,",")
comma <- lapply(comma,'[',1)
comma <- data.frame(commaLoc=unlist(comma))
#str_sub(d,1,comma$commaLoc)


#find second comma
comma2 <- str_locate_all(d,",")
comma2 <- lapply(comma2,'[',2)
comma2 <- data.frame(comma2Loc=unlist(comma2))
#str_sub(d,1,comma2$comma2Loc)


#extract name
matches <- cbind(period,char,comma,comma2)
matches$min <- apply(matches[,c(1,4)],1,min,na.rm=T)
names <- data.frame(Name=str_sub(d,1,matches$min))


#extract chair
chair <- str_locate_all(d,"Chaired")
chair <- lapply(chair,'[',1)
chair <- data.frame(chairLoc=unlist(chair))
chairLoc <- chair
chair <- str_sub(d,chair$chairLoc,yearloc$yearLoc-1)
chair <- str_trim(chair)
chair <- str_replace(chair,"Chaired by","")
chair <- str_replace(chair,"Chaired","")
chair <- str_replace(chair,"by","")
chair <- str_trim(chair)
chair <- gsub('January|February|March|April|May|June|July|August|September|October|November|December',
              '',chair)
chair <- str_trim(chair)
chair <- str_replace_all(chair,"[[:punct:]]","")
chair <- str_replace_all(chair,"\\t","")
chair <- str_replace_all(chair,"Dr","")
chair <- str_replace_all(chair,"PhD","")
chair <- str_replace_all(chair,"    ","")
chair <- str_trim(chair)


##Institution
inst <- str_sub(d,yearloc$yearLoc+4,str_length(d))
inst <- str_replace_all(inst,"[[:punct:]]","")
inst <- gsub("[[:digit:]]","",inst)
#inst <- gsub("[^[:alnum:]]","",inst)
inst <- str_trim(inst)
inst <- gsub("chaired by","",inst)
inst <- gsub("chaired","",inst)
inst <- gsub("by","",inst)
inst <- data.frame(inst)


##Geocode them
univ <- data.frame(inst=unique(inst))
univ$inst <- as.character(univ$inst)
univ$inst <- gsub('CUNY Graduate Center','New York City,NY',univ$inst)
univ <- na.omit(univ)


#geo <- geocode(univ$inst) 
#saveRDS(geo,'geo.rds')
geo <- readRDS('geo.rds')
univ <- cbind(univ,geo)
names(univ) <- c('inst','lon','lat')
inst <- left_join(inst,univ,by='inst')



##title
title <- str_sub(d,matches$min,chairLoc$chairLoc)
title <- str_replace_all(title,"[[:punct:]]","")
#title <- str_trim(title)
#title <- gsub("[^[:alnum:]]","",title)
title <- data.frame(Title=title)



data <- cbind(years,names,chair,inst,title)
# missmap(data)
# Desc(data)
saveRDS(data,'Clean Grads2.rds')
rm(list=ls())


```

## Analysis
This plot shows the number of cases with missing data, and for which variables data is missing.  Latitude and longitude are the most problematic.  I had trouble parsing out the chair from the institution, and in some instances (CUNY Graduate Center), google did not recognize the institution and did not geocode.

```{r}

  
g <- readRDS("c:/users/connor/Desktop/ASCScraping/Clean Grads2.rds")
g <- g %>% filter(Year>2002) %>%   filter(Year<2016)

missmap(g,col=c('dimgrey','dodgerblue'))

```

##Locations
Some of these locations were not properly geocoded.  You can still see the volume in the New York area, Michigan, Omaha, and Los Angeles.
```{r}

  
gjs <- g %>% 
  select(inst,lat,lon) %>% 
  filter(!lon=='NA') %>%
  group_by(inst,lon=round(lon,5),lat=round(lat,5)) %>% 
  summarise(num=n())


inst <- gjs %>% group_by(lon,lat) %>% arrange(-num) %>% filter(row_number()==1)


test <- left_join(gjs,inst,by=c('lon','lat')) %>% 
  ungroup() %>%
  select(inst.y,lon,lat,num.y) %>%
  unique()




leaflet() %>% 
  addProviderTiles("CartoDB.Positron") %>%
  #addTiles() %>% 
  setView(lat=40.95,lng=-96.58,zoom=4) %>% 
  addCircleMarkers(lng=~lon,lat=~lat,radius=~num.y/2,
                   data=test,
                   popup=~inst.y)










```

## Wordcloud
It had to be done.  These are trite plots, but also a good first step in examining text data.  Perhaps not surprisingly, police (and related variants) is the most common term.  And by a longshot.
```{r,warning=F,fig.width=8,fig.height=8}


my_stop_words <- data.frame(word=c('univers','graduate','social','florida','houston',
                                     'michael','john','college','jay',
                                     'university','chaired','criminal','august','state',
                                     'may','december','crime','justice','the',
                                     'study','analysis','examination','and','the',
                                     '\\?','\\???','o','othe','use','among'))


gtidy <- g %>% 
  dplyr::select(Title) %>% 
  mutate(Title=as.character(Title)) %>% 
  na.omit() %>% 
  unnest_tokens(word,Title) %>% 
  anti_join(stop_words) %>% 
  anti_join(my_stop_words)

gtidy %>% 
  count(word) %>% 
  with(wordcloud(word,n,max.words=250))



  #findFreqTerms(term.matrix,20)
  
 
top20 <- 
gtidy %>% 
  count(word) %>%  
  arrange(-n) %>%
  top_n(20)

top20

top20 %>% 
  mutate(word=reorder(word,n)) %>% 
  ggplot(aes(word,n))+geom_bar(stat='identity')+
  coord_flip()+
  theme_minimal()+
  labs(title='Top 20 Terms in CJ Dissertations',
       x='Mentions in Dissertation Titles')






```


## Word Association
TM has a great function, ```findAssocs() ```.  This function returns a list of words with a minimum specified correlation to the input word.  'Risk' is strongly associated with modeling, testing, and instruments.  The 'police' search also show the influence of public facing actions - contact and situations.    
```{r,echo=T,warning=F}


ds <- VectorSource(na.omit(as.character(g$Title)))

  
  
  term.matrix <- TermDocumentMatrix(Corpus(ds),
                     control=list(removePunctuation=T,
                                  tolower=T,
                                  removeNumbers=T,
                                  stopwords=T))
  

findAssocs(term.matrix,"risk",.2)
findAssocs(term.matrix,"police",.2)

```


## Tidy Text
This a package from David Robinson and Julia Silge.  Some examples straight from their vignettes.  Risk, offender, violent, delinquency, and prison have the most negative sentiment, while work, support,intimate, fairness and trust are mostly positive.  


```{r}


bing <- sentiments %>% 
  filter(lexicon=='bing') %>% 
  select(-score)


sent <- tidy(term.matrix) %>% 
  inner_join(bing, by=c(term='word')) %>% 
  count(term,sentiment,wt=count) %>% 
  arrange(-n) %>% filter(n>2) %>% 
  ungroup() %>% 
  spread(sentiment,n,fill=0) %>% 
  mutate(sentiment=positive-negative) %>% 
  arrange(sentiment)


sent %>%
  mutate(term=reorder(term,sentiment)) %>%
  ggplot(aes(term,sentiment,fill=sentiment))+geom_bar(stat='identity')+
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  ggtitle('Term Sentiment')


  ggplot(sent,aes(x=negative,y=positive,group=term))+geom_jitter() +
  geom_text(aes(label=term),check_overlap = T)



```

##Conclusion
This quick analysis shows the prevalence of police-related research.  I was surprised how low the term 'risk' ranked.  I supposed dissertationmight often deal with risk of a certain outcome, but not necessarily mention it in the title. I became a bit more comfortable with some text packages, so it was all worth it.

```{r,echo=F,include=F} 


## TF-IDF
# Term frequency-inverse document frequency is a weight used to measure how important a particular word is to a document in a collection. There is still some cleaning left to do, but this indicates that terms like 'police' and 


  words <- tidy(term.matrix) %>%
  mutate(total=sum(count)) %>% 
  bind_tf_idf(term,document,count) %>% 
  select(-total) %>% 
  arrange(tf_idf) %>% 
  select(-count,-tf) %>% 
  unique() %>% 
  arrange(tf_idf)


words



```

